---
title: "Home Work 5"
author: "Nicholas Nasser"
date: "GitHub Repository Link - https://github.com/sous20/HW_5"
output: pdf_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggplot2)
library(mosaic)
library(stringr)
library(kableExtra)
options(scipen = 999)

letters = read.csv("letter_frequencies.csv")

```

## Problem 1

&nbsp;

```{r, results = FALSE}

sim_iron = do(100000)*nflip(n = 2021, prob = 0.024)

```

*Null Hypothesis -* For this scenario, the null hypothesis I am testing is that the rate at which legal trades by Iron Bank employees are flagged by the SEC is equal to the baseline rate of 2.4% for all other traders.

&nbsp;

*Test Statistic -* The test statistic I used to measure evidence against the null hypothesis was the number of Iron Bank trades flagged by the SEC.

&nbsp;

```{r, results = FALSE, fig.height = 3.5, fig.width = 6, fig.align = "center"}

ggplot(sim_iron) + geom_histogram(aes(x = nflip), binwidth = 1, color = "black", fill = "khaki") + labs(title = "Probability Distribution of Flagged Trades", x = "Number of Flagged Trades", y = "Count")

sum(sim_iron$nflip >= 70) / 100000

```

&nbsp;

*P-Value -* The p-value for this probability distribution (given that we are looking only at generated samples where the number of flagged trades was 70 or higher) is `r sum(sim_iron$nflip >= 70) / 100000`.

&nbsp;

*Conclusion -* In light of the data, I feel that the null hypothesis does not fully explain the proportion of Iron Bank trades that were flagged by the SEC ($70/2021 \approx 3.46$%) because of the low p-value generated from the probability distribution. Despite this, I still believe that the Iron Bank should be investigated further before concluding that the null hypothesis is false since the distribution did contain values of 70 or more (albeit rarely).

\newpage

## Problem 2

&nbsp;

```{r, results = FALSE}

sim_gourmet = do(100000)*nflip(n = 50, prob = 0.03)

```

*Null Hypothesis -* For this specific scenario, the null hypothesis I am testing is that the rate at which Gourmet Bites locations receive health code violations is the same as the baseline rate of 3% at which all restaurants receive violations due to random issues.

&nbsp;

*Test Statistic -* The test statistic I used to measure evidence against the null hypothesis was the number of health code violations for Gourmet Bites locations.

&nbsp;

```{r, results = FALSE, fig.align = "center"}

ggplot(sim_gourmet) + geom_histogram(aes(x = nflip), binwidth = 1, color = "black", fill = "khaki") + scale_x_continuous(breaks = 0:9) + labs(title = "Probability Distribution of Locations in Violation of Health Codes", x = "Number of Locations", y = "Count")

sum(sim_gourmet$nflip >= 8) / 100000

```

&nbsp;

*P-Value -* The p-value for this probability distribution (given that we are looking only at generated samples where the number of Gourmet Bites health code violations was 8 or more) is `r sum(sim_gourmet$nflip >= 8) / 100000`.

&nbsp;

*Conclusion -* In light of the data, I feel that the null hypothesis does not fully explain the proportion of Gourmet Bites locations that received health code violations (8/50 = 16%) because of the low p-value generated from the probability distribution. Despite this, I still feel that Gourmet Bites should be further investigated before concluding that the null hypothesis is false, since values of 8 or more health violations did show up in the distribution (albeit rarely).

\newpage

## Problem 3

```{r, results = FALSE, warning = FALSE}

brown = readLines("brown_sentences.txt")

brown = toupper(gsub("[^A-Za-z]", "", brown))

counts = lapply(brown, function(sentence) {
  
  table(factor(unlist(strsplit(sentence, ""), use.names = FALSE), levels = letters$Letter))
  
})

counts = as.data.frame(do.call(rbind, counts))

expected_values = lapply(brown, function(sentence) {
  letters$Probability * nchar(sentence)
})
expected_values = as.data.frame(do.call(rbind, expected_values))

chi_squared = rowSums((counts - expected_values)^2 / expected_values)

sentences = c(
  "She opened the book and started to read the first chapter, eagerly anticipating what might come next.",
  "Despite the heavy rain, they decided to go for a long walk in the park, crossing the main avenue by the fountain in the center.",
  "The museum’s new exhibit features ancient artifacts from various civilizations around the world.",
  "He carefully examined the document, looking for any clues that might help solve the mystery.",
  "The students gathered in the auditorium to listen to the guest speaker’s inspiring lecture.",
  "Feeling vexed after an arduous and zany day at work, she hoped for a peaceful and quiet evening at home, cozying up after a quick dinner with some TV, or maybe a book on her upcoming visit to Auckland.",
  "The chef demonstrated how to prepare a delicious meal using only locally sourced ingredients, focusing mainly on some excellent dinner recipes from Spain.",
  "They watched the sunset from the hilltop, marveling at the beautiful array of colors in the sky.",
  "The committee reviewed the proposal and provided many points of useful feedback to improve the project’s effectiveness.",
  "Despite the challenges faced during the project, the team worked tirelessly to ensure its successful completion, resulting in a product that exceeded everyone’s expectations."
)

sentences = toupper(gsub("[^A-Za-z]", "", sentences))

counts_sentences = lapply(sentences, function(sentence) {
  
  table(factor(unlist(strsplit(sentence, ""), use.names = FALSE), levels = letters$Letter))
  
})

counts_sentences = as.data.frame(do.call(rbind, counts_sentences))

sentences_expected = lapply(sentences, function(sentence) {
  
  letters$Probability * nchar(sentences)
  
})
sentences_expected = as.data.frame(do.call(rbind, sentences_expected))

chi_sentences = rowSums((counts_sentences - sentences_expected)^2 / sentences_expected)

p_values = sapply(chi_sentences, function(chi_sentence) {
  round(sum(chi_squared >= chi_sentence) / length(chi_squared), 4)
})

chi_table = rbind(paste("Sentence", seq_along(sentences)), p_values)

```

```{r}

chi_table %>%
  
kbl(caption = "Chi Squared Statistics for Each Sentence") %>%
    
  kable_styling(latex_options = "hold_position") %>%
  
  column_spec(1:ncol(chi_table), width = "1.2cm")
  

```


